%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Dgraph Labs} % Organization
    {Remote - Bengaluru, India} % Location
    {Dec. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, built and maintained a declarative schema driven, auto-generated, GraphQL API layer on top of Dgraph, with a vision to interface a UI application directly to Dgraph without the need of an intermediate backend.}
	\item {Added support for integrating custom business logic, including JavaScript lambda functions to support serverless deployments.}
	\item {Discovered and solved various concurrency issues around GraphQL schema storage, and long-standing bugs in enterprise backup-restore functionality.}
	\item {Optimized GraphQL auth query generation, resulting in a 10x improvement in query latency.}
	\item {Benchmarked and optimized the whole GraphQL layer to account for only 0.13\% of query execution time, adding an improvement of 33\% in overall query latency.}
	\item {Helped design and integrate Apollo Federation support into the GraphQL API, enabling Dgraph to be used with other GraphQL services in a ecosystem.}
	\item {Helped team members with understanding the codebase, PR reviews and feature documentation.}
	\item {Maintaining dgraph4j - a gRPC based Dgraph client for Java.}
	\item {Working on an automated flow for importing data from PostgreSQL to Dgraph Cloud.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer, CyberSecurity} % Job title
    {Visa Inc.} % Organization
    {Bengaluru, India} % Location
    {Jul. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {API DAST}
	  \begin{itemize}
	    \item {Developed a command-line tool from scratch to perform automated Dynamic Application Security Testing of APIs for OWASP Top 10 risks like SQL injection, TLS validation, etc.}
	    \item {Designed extensible authentication framework in tool for scanning APIs requiring authentication.}
	    \item {Automated API discovery using OpenAPI specification.}
	  \end{itemize}
        \item {SHIFTLEFT}
	  \begin{itemize}
	    \item {A micro-service architecture based multi-module internal RBAC web-application for automating CyberSecurity interaction with other teams.}
	    \item {Developed 2 new Spring Boot modules for automating tasks performed by different groups within CyberSecurity.}
	    \item {Developed the UI for the new modules in Angular.}
	  \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Google Summer of Code Contributor} % Job title
    {VideoLAN} % Organization
    {Remote - Paris, France} % Location
    {Jun. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to VLMC (VideoLAN Movie Creator), an open-source, cross-platform, non-linear editing software for video creation based on libVLC.}
	\item {Setup the android build and refactored some UI components using QML to be responsive to screen size.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Edurer Knowledge Labs} % Organization
    {Jodhpur, India} % Location
    {Dec. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a cross-platform app using Meteor framework for α–release.}
	\item {Developed an iOS app for β–release of Edurer.}
	\item {Developed an Android app for product launch.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
